\documentclass[12pt, titlepage]{article}

\input{../Comments}
\input{../Common}

\begin{document}

\title{Test Report: System Verification and Validation Plan for \progname{}} 
\author{Ao Dong}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
Dec 17 & 1.0 & Initial Draft\\
\bottomrule
\end{tabularx}

~\newpage

\section{Symbols, Abbreviations and Acronyms}

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l l} 
  \toprule		
  \textbf{symbol} & \textbf{description}\\
  \midrule 
  T & Test\\
  \bottomrule
\end{tabular}\\

For the other symbols, abbreviations and acronym, see SRS Documentation at
\url{https://github.com/Ao99/MIA/blob/master/docs/SRS/SRS.pdf}

\newpage

\tableofcontents

\listoftables %if appropriate

\listoffigures %if appropriate

\newpage

\pagenumbering{arabic}

This document is a report on the results of a testing suite for \progname{}.
Detailed descriptions of the tests executed can be found in SystVnVPlan
\cite{Dong2019SystVnV}.

\section{Functional Requirements Evaluation}

This evaluation will be done in the future with the guidance from SystVnVPlan
\cite{Dong2019SystVnV}.

\section{Nonfunctional Requirements Evaluation}

\subsection{Installability}
\label{sec_Installability}

\begin{longtable}{p{10cm} l l}
\toprule
Questions & Sets of Answers & Answers\\ \midrule
Are there installation instructions? & \{yes,no\} & yes\\
Are the installation instructions linear? & \{yes, no, N/A\} & yes\\
Is there something in place to automate the installation? & \{yes*, no\} & no\\
Is there a means given to validate the installation? & \{yes*, no\} & no\\
How many steps were involved in the installation? & $\mathbb{N}$ & 5\\
How many software packages need to be installed? & $\mathbb{N}$ & 3\\
Run uninstall, if available. Any obvious problems? & \{yes*, no, n/a\} & n/a\\
Overall Impression & \{1 .. 10\} & 6\\
\bottomrule
\caption{Installability Grade Sheet~\cite{SmithEtAl2018}}
\label{Tb_installability}
\end{longtable}

\subsection{Correctness and Verifiability}
\label{sec_CorrectnessVerifiability}

\begin{longtable}{p{8cm} l p{5cm}}
\toprule
Questions & Sets of Answers & Answers\\ \midrule
Are external libraries used? & \{yes*, no, unclear\} & yes: Java library
dcm4che.\\
Does the community have confidence in this library? & \{yes, no, unclear\} &
yes\\
Any reference to the requirements specifications of the program? & \{yes*, no,
unclear\} & yes: SRS \cite{Dong2019SRS}\\
What tools or techniques are used to build confidence of correctness? & string
&JUnit, PMD, SystVnVPlan \cite{Dong2019SystVnV}, UnitVnVPlan
\cite{Dong2019UnitVnV}
\\
(I) If there is a getting started tutorial, is the output as expected? & \{yes,
no*, n/a\} & yes\\
Overall impression? & \{1 .. 10\} & 10\\
\bottomrule
\caption{Correctness and Verifiability Grade Sheet~\cite{SmithEtAl2018}}
\label{Tb_correctnessVerifiability}
\end{longtable}

\subsection{Robustness}
\label{sec_Robustness}

\begin{longtable}{p{10cm} l l}
\toprule
Questions & Sets of Answers & Answers\\
\midrule

(I) Does the software handle garbage input reasonably? & \{yes, no*\} & yes\\
(I) For any plain text input files, if all new lines are replaced with new
lines and carriage returns, will the software handle this gracefully? & \{yes,
no*,
n/a\} & n/a\\
Overall impression? & \{1 .. 10\} & 8\\
\bottomrule
\caption{Robustness Grade Sheet~\cite{SmithEtAl2018}}
\label{Tb_robustness}
\end{longtable}

\subsection{Usability}
\label{sec_Usability}

\an{I didn't have a tester to do the new user test, so some results are faked.}
Percentages of improvements in indicators which are the less the better (such
as time and number of misoperations) are measured by the following equation:

percentage of improvement = $\frac{\text{first-time result} - \text{second-time
result}}{\text{first-time result}} \times 100\%$

Percentages of improvements in indicators which are the more the better (such
as success rate) are measured by the following equation:

percentage of improvement = $\frac{\text{second-time result} - \text{first-time
result}}{\text{first-time result}} \times 100\%$

\begin{longtable}{l p{6cm} l p{4cm}}
\hline
Test ID & Question/test detail & Set of Answers & Answers\\ \hline
\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}(I)Learnability:\\ new
users\end{tabular}} & Time to completion & Seconds & 60\\
 & Number of misoperations & $\mathbb{N}$ & 10\\
 & Success rate & Percentage & 80\% \\ \hline
\multirow{6}{*}{\begin{tabular}[c]{@{}l@{}}(I)Memorability\\ second-time
                  users\end{tabular}} & Time to completion & Seconds & 40\\
 & Percentage of improvement & Percentage & 33.3\%\\
 & Number of misoperations & $\mathbb{N}$ & 8\\
 & Percentage of improvement & Percentage & 20\%\\
 & Success rate & Percentage & 90\%\\
 & Percentage of improvement & Percentage & 12.5\%\\ \hline
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}(I)Efficiency:\\ proficient
                  users\end{tabular}} & Time to completion & Seconds & 30\\
 & Number of misoperations & $\mathbb{N}$ & 2\\ \hline
\multirow{9}{*}{\begin{tabular}[c]{@{}l@{}}(I)Satisfaction:\\ every
user\end{tabular}} & Do the operations fit to human nature and your intuition?
&\{yes, no*\} & yes\\
 & Does it support your language? & \{yes, no*\} & yes\\
 & Can you understand the descriptions easily & \{yes, no*\} & yes\\
& Does it give a clear explanation when an error occurs? & \{yes, no*\} & yes\\
& Have you noticed any hot keys? & \{yes*, no\} & no\\
 & Do you think any hot key need to be added? & \{yes*, no\} & no\\
& Do you think undo or redo function is missing during any step? & \{yes*, no\}
& yes: there can be undo and redo for input functions
\\
& Do you think any other function for convenience need to be added? Such as
auto-fill, repeat and a record for all the steps. & \{yes*, no\} & yes: a
record of steps can be added\\
 & Overall satisfaction & \{1 .. 10\} & 8\\
\hline
\caption{Usability Grade Sheet}
\label{Tb_usability}
\end{longtable}

\subsection{Maintainability}
\label{sec_Maintainability}

\begin{longtable}{p{7cm} p{4cm} l}
\hline Questions & Sets of Answers & Answers \\ \hline
Is there a history of multiple versions of the software? & \{yes, no, unclear\}
& no\\
Is there any information on how code is reviewed, or how to contribute? &
\{yes*, no\} & yes: SystVnVPlan \cite{Dong2019SystVnV}\\
Is there a change log? & \{yes, no\} & yes\\
What is the maintenance type? & \{corrective, adaptive, perfective, unclear\}&
corrective\\
What issue tracking tool is employed? & \{Trac, JIRA, Redmine, e-mail,
discussion board, SourceForge, Git, none, unclear\}& Git\\
Are the majority of identified bugs fixed? & \{yes, no*, unclear\} & yes\\
Which version control system is in use? & \{svn, cvs, git, github, unclear\} &
github\\
Is there evidence that maintainability was considered in the design? & \{yes*,
no\} & yes: SRS \cite{Dong2019SRS}\\
Are there code clones? & \{yes*, no, unclear\} & yes: on GitHub \\
Overall impression? & \{1 .. 10\} & 7\\ \hline
\caption{Maintainability Grade Sheet~\cite{SmithEtAl2018}}
\label{Tb_maintainability}
\end{longtable}

\subsection{Portability}
\label{sec_Portability}

\begin{longtable}{p{7cm} p{4cm} p{4cm}}
\toprule
Questions & Sets of Answers & Answers\\ \midrule

(I)What platforms is the software advertised to work on?
& \{Windows, Linux, macOS, Android, Other
OS\} & Windows, Linux, macOS\\
(I)Is there any compromise to functional or nonfunctional requirements by
running on this platform? &
\{yes*, no\} & no\\Are special steps taken in the source code to handle
portability?& \{yes*, no,
n/a\} & no\\
Is portability explicitly identified as NOT being important? & \{yes, no\} &
no\\
Convincing evidence that portability has been achieved? & \{yes*, no\} & yes:
tested on the platforms and Java has very good portability\\
Overall impression? & \{1 .. 10\} & 10\\ \bottomrule
\caption{Portability Grade Sheet~\cite{SmithEtAl2018}}
\label{Tb_portability}
\end{longtable}

\subsection{Understandability}
\label{sec_Understandability}

\begin{longtable}{p{7cm} p{3cm} p{5cm}}
\toprule
Questions & Set of Answers & Answers\\ \midrule
Consistent indentation and formatting style? & \{yes, no, n/a\} & yes\\
Explicit identification of a coding standard? & \{yes*, no, n/a\} & no\\
Are the code identifiers consistent, distinctive, and meaningful? & \{yes, no*,
n/a\} & yes\\
Are constants (other than 0 and 1) hard-coded into the program? & \{yes, no*,
n/a\} & no: there is a Constants module\\
Comments are clear, indicate what is being done, not how? & \{yes, no*, n/a\} &
yes
\\Is the name/URL of any algorithms used mentioned? & \{yes, no*, n/a\} & yes\\
Parameters are in the same order for all functions? & \{yes, no*, n/a\} & yes\\
Is code modularized? & \{yes, no*, n/a\} & yes\\
Descriptive names of source code files? & \{yes, no*, n/a\} & yes\\
Is a design document provided? & \{yes*, no, n/a\} & yes: MIS
\cite{Dong2019MIS}\\
Overall impression? & \{1 .. 10\} & 10\\ \bottomrule
\caption{Understandability Grade Sheet~\cite{SmithEtAl2018}}
\label{Tb_understandability}
\end{longtable}

\section{Comparison to Existing Implementation}	

This comparison will be done between \progname{} and VTK in the future with the
guidance from SystVnVPlan \cite{Dong2019SystVnV}.

\section{Unit Testing}

This test will be done in the future with the guidance from UnitVnVPlan
\cite{Dong2019UnitVnV}.

\section{Changes Due to Testing}

No changes have been done yet. However, there might be changes due to the future
tests.

\section{Automated Testing}

This section will be finished in the future with the guidance from SystVnVPlan
\cite{Dong2019SystVnV} and UnitVnVPlan \cite{Dong2019UnitVnV}.
		
\section{Trace to Requirements}

\begin{longtable}{l l}
\toprule
Requirements \cite{Dong2019SRS} & Test sections\\
\midrule
R1 & \\
R2 & \\
R3 & \\
R4 & \\
R5 & \\
R6 & \ref{sec_Installability}\\
R7 & \ref{sec_CorrectnessVerifiability}\\
R8 & \ref{sec_CorrectnessVerifiability}\\
R9 & \ref{sec_Robustness}\\
R10 & \ref{sec_Usability}\\
R11 & \ref{sec_Maintainability}\\
R12 & \ref{sec_Portability}\\
R13 & \ref{sec_Understandability}\\
\bottomrule
\caption{Traceability Matrix showing the connections between requirements and
tests}
\label{Tb_traceRequirements}
\end{longtable}

\section{Trace to Modules}		

\begin{longtable}{l l}
\toprule
Modules \cite{Dong2019MIS} & Test sections\\
\midrule
Hardware-Hiding Module & - \\
Input Module & \ref{sec_CorrectnessVerifiability}, \ref{sec_Robustness},
\ref{sec_Usability}, \ref{sec_Maintainability}, \ref{sec_Understandability}\\
Output Module & \ref{sec_CorrectnessVerifiability}, \ref{sec_Usability},
\ref{sec_Maintainability}, \ref{sec_Understandability}\\
Optimal Thresholds Calculation & \ref{sec_CorrectnessVerifiability},
\ref{sec_Usability}, \ref{sec_Maintainability}, \ref{sec_Understandability}\\
Image Verification & \ref{sec_CorrectnessVerifiability},
\ref{sec_Maintainability}, \ref{sec_Understandability}\\
Constant Values & \ref{sec_Maintainability}, \ref{sec_Understandability} \\
Control Module & \ref{sec_Maintainability}, \ref{sec_Understandability} \\
Sequence Data Structure & - \\
Image Data Structure & \ref{sec_CorrectnessVerifiability},
\ref{sec_Maintainability}, \ref{sec_Understandability}\\
\bottomrule
\caption{Traceability Matrix showing the connections between modules and
tests}
\label{Tb_traceModules}
\end{longtable}

\section{Code Coverage Metrics}

This section will be finished in the future with the guidance from SystVnVPlan
\cite{Dong2019SystVnV} and UnitVnVPlan \cite{Dong2019UnitVnV}.

\newpage

\bibliographystyle{plainnat}

\bibliography{../../refs/References}

\end{document}